Real World Manuscript Analyses

### 2022-04-21 RWE/RWE Manuscript analyses.Rmd
Update

@@

  # mutate(`Anemia_7d` = case_when(
  #   `Hb day +7` < 11.4                                              ~ "YES",
  #   is.na(`Hb day +7`)                                          ~ NA_character_,

@@

  # mutate(`Anemia_30d` = case_when(
  #   `Hb day +30` < 11.4                                             ~ "YES",
  #   is.na(`Hb day +30`)                                          ~ NA_character_,
  # mutate(`Anemia_60d` = case_when(
  #   `Hb day +60` < 11.4                                             ~ "YES",
  #   is.na(`Hb day +60`)                                          ~ NA_character_,
  # mutate(`Anemia_90d` = case_when(
  #   `Hb day +90` < 11.4                                             ~ "YES",
  #   is.na(`Hb day +90`)                                          ~ NA_character_,

@@

  # mutate(`gr3_Anemia_7d` = case_when(
  #   `Hb day +7` < 8                                              ~ "YES",
  #   is.na(`Hb day +7`)                                          ~ NA_character_,

@@

  # mutate(`gr3_Anemia_30d` = case_when(
  #   `Hb day +30` < 8                                             ~ "YES",
  #   is.na(`Hb day +30`)                                          ~ NA_character_,
  # mutate(`gr3_Anemia_60d` = case_when(
  #   `Hb day +60` < 8                                             ~ "YES",
  #   is.na(`Hb day +60`)                                          ~ NA_character_,
  # mutate(`gr3_Anemia_90d` = case_when(
  #   `Hb day +90` < 8                                             ~ "YES",
  #   is.na(`Hb day +90`)                                          ~ NA_character_,

@@

  #     `Hb day +30` < 11.4 | 

@@

  #     is.na(`Hb day +30`) |

@@

  #     `Hb day +30` < 8 | 

@@

  #     `Hb day +90` < 8 | 

@@

  #     is.na(`Hb day +90`) |

@@

## Table 1. Patient baseline characteristics
```{r}
cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`, 
         # cyto, 
         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Prior auto SCT (yes, no)`, 
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         `Did patient met criteria for KarMMa1 pre-CAR-T?`) %>% 
  tbl_summary(
    type = list(
      c(`Extramedullary Disease? (Yes, No)`, `High Marrow Burden (>= 50%)`,
    #     cyto, 
    `Deletion 17p prior to CAR-T infusion (yes, no)`,
        `t(4:14) prior to CAR-T infusion (yes, no)`,
        `t(14:16) prior to CAR-T infusion (yes, no)`,
        `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
        immuno, proteasome, dara, doubleref, tripleref, pentaref,
        `Did patient met criteria for KarMMa1 pre-CAR-T?`)
      ~"categorical"),

@@

## Table 2. Clinical outcomes
**best response**
```{r}
tbl1 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(`Max CRS grade (0-5)`,
         # `Day of onset of CRS relative to infusion`,
         `Day of Max CRS (relative to infusion)`,

         `Max ICANS (relative to infusion)`,
         # `Day of onset of ICANS relative to infusion`,
         `Day of Max ICANS (relative to infusion)`) %>% 
  tbl_summary(type = list(
    c(
      `Day of Max ICANS (relative to infusion)`) ~ "continuous"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1,
    missing = "no") %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)

tbl2 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(`Steroid use (Yes, No)`, `Tocilizumab (Yes, No)`, 
         `Anakinra (Yes, No)`) %>% 
  tbl_summary(type = list(
    c(`Steroid use (Yes, No)`, `Tocilizumab (Yes, No)`, 
      `Anakinra (Yes, No)`) ~ "categorical"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1) %>% 
  bold_labels() %>% add_stat_label()

tbl3 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(#MRDneg_30days,
         ORR_30days,
         day30_response,
         day30_response_group) %>% 
  tbl_summary(#type = list(
    # c(MRDneg_30days) ~ "categorical"),
    digits = all_continuous() ~ 1,
    missing = "no") %>% 
  bold_labels() %>% add_stat_label()

# tbl4 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(day30_response_group == "CR or sCR") %>% 
#   select(MRDneg_30days) %>% 
#   tbl_summary(type = list(c(MRDneg_30days) ~ "categorical"),
#               label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
#               digits = all_continuous() ~ 1,
#               missing = "no") %>% 
#   bold_labels() %>% add_stat_label()

tbl5 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(#MRDneg_90days,
         ORR_90days,
         day90_response,
         day90_response_group) %>% 
  tbl_summary(#type = list(
    # c(MRDneg_90days) ~ "categorical"),
    digits = all_continuous() ~ 1,
    missing = "no") %>% 
  bold_labels() %>% add_stat_label()

# tbl6 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(day90_response_group == "CR or sCR") %>% 
#   select(MRDneg_90days) %>% 
#   tbl_summary(type = list(c(MRDneg_90days) ~ "categorical"),
#               label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
#               digits = all_continuous() ~ 1,
#               missing = "no") %>% 
#   bold_labels() %>% add_stat_label()

tbl7 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(best_response) %>% 
  tbl_summary(#type = list(c(MRDneg_90days) ~ "categorical"),
              label = list(best_response ~ "best response in the first 90 days"),
              digits = all_continuous() ~ 1,
              missing = "no") %>% 
  bold_labels() %>% add_stat_label()

tbl8 <- cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  filter(best_response == "CR or sCR") %>% 
  select(MRDneg_in_best_response) %>% 
  tbl_summary(type = list(c(MRDneg_in_best_response) ~ "categorical"),
              label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1,
              missing = "no") %>% 
  bold_labels() %>% add_stat_label()

tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) %>% as_gt() %>%
  gt::tab_source_note(gt::md("**
                             **"))

@@

Hb_fig <-
  data.frame(timepoints, t(round(
    sapply(cart2[, c(
      "Hb apheresis",
      "Hb day -5 (k/ul)",
      "Hb day 0 (k/uL)",
      "Hb day +7",
      "Hb day +14",
      "Hb day +21",
      "Hb day +30",
      "Hb day +60",
      "Hb day +90"
    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
  )))
Hb_fig <- Hb_fig %>% 
  ggplot(aes(x = timepoints, y = median)) + 
  geom_line(col = "blue") + 
  xlab("Days relative to infusion") + 
  ylab("Median Hb") + 
  theme_classic() + 
  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
  scale_x_continuous(
    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
  ) + 
  ylim(7.5, 12)

>>>>

  mutate(`Length of Hospital Stay (Total Days including Readmission)` =
           as.numeric(`Length of Hospital Stay (Total Days including Readmission)`)) %>% 

@@

  mutate(`Anemia_7d` = case_when(
    `HgB Day 7` < 11.4                                              ~ "YES",
    is.na(`HgB Day 7`)                                          ~ NA_character_,

@@

  mutate(`Anemia_30d` = case_when(
    `HgB Day 30` < 11.4                                             ~ "YES",
    is.na(`HgB Day 30`)                                          ~ NA_character_,
  mutate(`Anemia_60d` = case_when(
    `HgB Day 60` < 11.4                                             ~ "YES",
    is.na(`HgB Day 60`)                                          ~ NA_character_,
  mutate(`Anemia_90d` = case_when(
    `HgB Day 90` < 11.4                                             ~ "YES",
    is.na(`HgB Day 90`)                                          ~ NA_character_,

@@

  mutate(`gr3_Anemia_7d` = case_when(
    `HgB Day 7` < 8                                              ~ "YES",
    is.na(`HgB Day 7`)                                          ~ NA_character_,

@@

  mutate(`gr3_Anemia_30d` = case_when(
    `HgB Day 30` < 8                                             ~ "YES",
    is.na(`HgB Day 30`)                                          ~ NA_character_,
  mutate(`gr3_Anemia_60d` = case_when(
    `HgB Day 60` < 8                                             ~ "YES",
    is.na(`HgB Day 60`)                                          ~ NA_character_,
  mutate(`gr3_Anemia_90d` = case_when(
    `HgB Day 90` < 8                                             ~ "YES",
    is.na(`HgB Day 90`)                                          ~ NA_character_,

@@

  #     `HgB Day 30` < 11.4 | 

@@

  #     is.na(`HgB Day 30`) |

@@

  #     `HgB Day 30` < 8 | 

@@

  #     `HgB Day 90` < 8 | 

@@

  #     is.na(`HgB Day 90`) |

@@

## Table X. Manufacturing failures
```{r}
MM_cart %>% 
  # Exclude patients who had manufacturing cart failure or died prior cart infusion
  select(`First manufacturing failure`, 
         `Manufaturing failures with successfull second collection`) %>% 
  mutate(across(everything(), ~ replace_na(., 0))) %>% 
  tbl_summary(
    statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
    digits = all_continuous() ~ 1,
    missing = "no"
  ) %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```
<br>

## Table 1. Patient baseline characteristics
```{r}
cart0 %>% 
  distinct(patient_id, .keep_all = TRUE) %>% 
  select(Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (Yes, No)`, 
         `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`,

         `High Marrow Burden (>= 50%)`, 
         `ECOG at consult`, `ECOG at LD`, 
         `R-ISS at CAR-T infusion`,

         `Deletion 17p prior to CAR-T infusion (yes, no)`,
         `t(4:14) prior to CAR-T infusion (yes, no)`,
         `t(14:16) prior to CAR-T infusion (yes, no)`,
         `Bridging Therapy? (Yes, No)`,
         `Number of prior lines of therapy`,
         `Disease status at time of referral (Relapsed vs Refractory)`,
         `Prior auto SCT (yes, no)`, 
         `ASCT within 12 weeks prior to apheresis (Yes, No)`,
         `Prior Allo SCT (Yes, No)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes, No)`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref,

         `Cell Dose (million cells)`,
         `ECOG > or = 2? (Yes, No)`,
         `ANC < 1000/uL (Yes, No)`,
         `Hemoglobin < 8 g/dL (Yes, No)`,
         `Platelets < 50K (Yes, No)`,

         `Non-secretory MM (Yes, No)`,

         `Did patient met criteria for KarMMa1 pre-CAR-T?`) %>% 
  tbl_summary(
    type = list(
      c(
      `Extramedullary Disease? (Yes, No)`, 
      `Plasma Cell Leukemia? (yes, no)`,
         `Amyloid? (yes, no)`,
         POEMS,
         `Non-secretory MM (Yes, No)`,
      `High Marrow Burden (>= 50%)`,
    # #     cyto, 
    `Deletion 17p prior to CAR-T infusion (yes, no)`,
        `t(4:14) prior to CAR-T infusion (yes, no)`,
        `t(14:16) prior to CAR-T infusion (yes, no)`,
    #     `Bridging Therapy? (Yes, No)`, `Prior auto SCT (yes, no)`,
        immuno, proteasome, dara, doubleref, tripleref, pentaref,
    #     `Did patient met criteria for KarMMa1 pre-CAR-T?`
    )
      ~"categorical"),

@@

## Table 2. Safety with Standard of Care Idecabtagene Vicleucel Event and Grade

```{r}
# tbl1 <- 
  cart0 %>% 
  select(`Max CRS grade (0-5)`,
         `Day of Max CRS (relative to infusion)`,
         `Max ICANS (relative to infusion)`,
         `Day of Max ICANS (relative to infusion)`,
         `Length of Hospital Stay (Total Days including Readmission)`,
         `ICU Admission? (Yes, No)`,
         `Tocilizumab (Yes, No)`,
         `Steroid use (Yes, No)`,
         `Anakinra (Yes, No)`,

         `Need for GCSF`,
         `Need for TPO Agonist`

         ) %>% 
  tbl_summary(
    # type = list(
    # c(
    #   `Length of Hospital Stay (Total Days including Readmission)`
    #   ) ~ "continuous"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max}) [{p25}, {p75}]"), 
    digits = all_continuous() ~ 1,
    missing = "no") %>% 
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)

# tbl2 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select(`Steroid use (Yes, No)`, `Tocilizumab (Yes, No)`, 
#          `Anakinra (Yes, No)`) %>% 
#   tbl_summary(type = list(
#     c(`Steroid use (Yes, No)`, `Tocilizumab (Yes, No)`, 
#       `Anakinra (Yes, No)`) ~ "categorical"),
#     statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#     digits = all_continuous() ~ 1) %>% 
#   bold_labels() %>% add_stat_label()
# 
# tbl3 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select(#MRDneg_30days,
#          ORR_30days,
#          day30_response,
#          day30_response_group) %>% 
#   tbl_summary(#type = list(
#     # c(MRDneg_30days) ~ "categorical"),
#     digits = all_continuous() ~ 1,
#     missing = "no") %>% 
#   bold_labels() %>% add_stat_label()
# 
# # tbl4 <- cart0 %>% 
# #   distinct(patient_id, .keep_all = TRUE) %>% 
# #   filter(day30_response_group == "CR or sCR") %>% 
# #   select(MRDneg_30days) %>% 
# #   tbl_summary(type = list(c(MRDneg_30days) ~ "categorical"),
# #               label = list(MRDneg_30days ~ "MRDneg_30days within CR/sCR"),
# #               digits = all_continuous() ~ 1,
# #               missing = "no") %>% 
# #   bold_labels() %>% add_stat_label()
# 
# tbl5 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select(#MRDneg_90days,
#          ORR_90days,
#          day90_response,
#          day90_response_group) %>% 
#   tbl_summary(#type = list(
#     # c(MRDneg_90days) ~ "categorical"),
#     digits = all_continuous() ~ 1,
#     missing = "no") %>% 
#   bold_labels() %>% add_stat_label()
# 
# # tbl6 <- cart0 %>% 
# #   distinct(patient_id, .keep_all = TRUE) %>% 
# #   filter(day90_response_group == "CR or sCR") %>% 
# #   select(MRDneg_90days) %>% 
# #   tbl_summary(type = list(c(MRDneg_90days) ~ "categorical"),
# #               label = list(MRDneg_90days ~ "MRDneg_90days within CR/sCR"),
# #               digits = all_continuous() ~ 1,
# #               missing = "no") %>% 
# #   bold_labels() %>% add_stat_label()
# 
# tbl7 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   select(best_response) %>% 
#   tbl_summary(#type = list(c(MRDneg_90days) ~ "categorical"),
#               label = list(best_response ~ "best response in the first 90 days"),
#               digits = all_continuous() ~ 1,
#               missing = "no") %>% 
#   bold_labels() %>% add_stat_label()
# 
# tbl8 <- cart0 %>% 
#   distinct(patient_id, .keep_all = TRUE) %>% 
#   filter(best_response == "CR or sCR") %>% 
#   select(MRDneg_in_best_response) %>% 
#   tbl_summary(type = list(c(MRDneg_in_best_response) ~ "categorical"),
#               label = list(MRDneg_in_best_response ~ "MRDneg_in_best_response within CR/sCR"),
#               statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
#               digits = all_continuous() ~ 1,
#               missing = "no") %>% 
#   bold_labels() %>% add_stat_label()
# 
# 
# 
# tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) %>% as_gt() %>%
#   gt::tab_source_note(gt::md("**
#                              **"))

@@

Hb_fig <-
  data.frame(timepoints, t(round(
    sapply(cart2[, c(
      "Hb apheresis",
      "Hb day -5 (k/ul)",
      "Hb day 0 (k/uL)",
      "HgB Day 7",
      "Hb day +14",
      "Hb day +21",
      "HgB Day 30",
      "HgB Day 60",
      "HgB Day 90"
    )], MedianCI, conf.level = 0.95, na.rm = TRUE), 9
  )))
Hb_fig <- Hb_fig %>% 
  ggplot(aes(x = timepoints, y = median)) + 
  geom_line(col = "blue") + 
  xlab("Days relative to infusion") + 
  ylab("Median Hb") + 
  theme_classic() + 
  geom_ribbon(aes(ymin = lwr.ci, ymax = upr.ci), alpha = 0.1) + 
  scale_x_continuous(
    breaks = c(-28, -5, 0, 7, 14, 21, 30, 60, 90),
    labels = c("Apheresis","-5", "0", "7", "14", "21", "30", "60", "90")
  ) + 
  ylim(7.5, 12)
